### 2021-04-29 shared/analysis.tex
Benchmark Example 7

\begin{document}
	\begin{figure}
		\begin{minted}{python}
	def progam1(inpt):
		prob, _ = inpt
		z = 0
		flip = 0
		while (flip == 0):
			d = bernoulli.rvs(size=1, p=prob)[0]
			if d:
				flip = 1
			else:
				z = z + 1
		return z

	assert(z > (1 - prob)/prob)
		\end{minted}
		\caption{Program listing for finding probabilistic \texttt{assert} violation.}
	\end{figure}
	\begin{figure}
		\begin{minted}{c}
	int main()
	{
		double prob;
		int d, z = 0, flip = 0;

		make_pse_symbolic(&flip, sizeof(flip), "flip_pse_sym", 0, 1);
		make_pse_symbolic(&prob, sizeof(prob), "prob_sym", 0, 1);
		klee_make_symbolic(&z, sizeof(z), "z_sym");
		klee_assume(z >= 0);

		std::random_device rd{};
		std::mt19937 rng{rd()};
		std::bernoulli_distribution rvs(prob);

		while (flip == 0) {
			int d = rvs(rng);
			if (d) {
				flip = 1;
			} else {
				// must be executed more 
				// for the assert to pass. 
				z += 1; 
			}
		}

		return 0;
	}
		\end{minted}
		\caption{\texttt{Translate()} of the program for testing the \texttt{assert}. }
	\end{figure}
	\begin{figure}
		\begin{minted}{c}
		long long int termCount = 50000, unroll = 2500;
		while (termCount--)
		{
			flip = 0;
			z = 0;
			scanf("%Lf", &prob);

			...

			while (flip == 0 && unroll--) {
				int d = rvs(rng);
				if (d) {
					flip = 1;
				} else { 
					z += 1; 
				}
				if (z > ((double)(1 - prob) / (prob)))
					win++;
				flip_runs++;
			}
			program_runs++;
		}
		\end{minted}
		\caption{\texttt{Translate()} of the program for testing the \texttt{assert}. }
	\end{figure}
	\begin{figure}
			\begin{minted}{python}
		(flip_pse_sym <= 1),
		(0 <= flip_pse_sym),
		(prob_sym <= 1),
		(0.000001 < prob_sym),
		(0 <= z_sym),

		FAIL : (z_sym * prob_sym - (1 - prob_sym) <= 0)
		\end{minted}
		\caption{Constraints without optimization step.}
	\end{figure}
	\begin{figure}
		\begin{minted}{python}
		(flip_pse_sym <= 1),
		(0 <= flip_pse_sym),
		(prob_sym <= 1),
		(0.000001 < prob_sym),
		(0 <= z_sym),

		FAIL : (z_sym * prob_sym - (1 - prob_sym) <= 0)
		optimize : maximize(prob_sym)
		\end{minted}
		\caption{Constraints with optimization step.}
	\end{figure}
	\begin{table}
		\centering
		\caption{Comparing \texttt{prob(p)} value to cases Vs \texttt{assert} status for \texttt{optimization} over \texttt{prob} value}
		\label{}
		\begin{tabular}{ c | c | c | c | c } 
			\toprule
			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
			\hline\hline
			49999 & 50000 & 0.9999990463 & 0 & 0.0000009537 \\ \hline 
			49999 & 50000 & 0.9999995232 & 0 & 0.0000004768 \\ \hline 
			49999 & 50000 & 0.9999998808 & 0 & 0.0000001192 \\ \hline 
			49999 & 50000 & 0.9999999991 & 0 & 0.0000000009 \\ \hline 
			49999 & 50000 & 1.0000000000 & 0 & 0.0000000000 \\ \hline 
			50000 & 50000 & 0.9999847412 & 0 & 0.0000152590 \\ \hline 
			50001 & 50000 & 0.9999694825 & 0 & 0.0000305184 \\ \hline 
			50003 & 50000 & 0.9998779298 & 0 & 0.0001220851 \\ \hline 
			50008 & 50000 & 0.9997558596 & 0 & 0.0002442000 \\ \hline 
			50016 & 50000 & 0.9995117192 & 0 & 0.0004885193 \\ \hline 
			50045 & 50000 & 0.9990234385 & 0 & 0.0009775161 \\ \hline 
			50822 & 50000 & 0.9843750156 & 0 & 0.0158729998 \\ \hline 
			53303 & 50000 & 0.9375000625 & 0 & 0.0666665956 \\ \hline 
			57237 & 50000 & 0.8750001250 & 0 & 0.1428569796 \\ \hline 
			99385 & 50000 & 0.5000005000 & 0 & 0.9999980000 \\ \hline 
			\bottomrule
		\end{tabular}
	\end{table}
	\begin{table}
		\centering
		\caption{Comparing \texttt{prob(p)} value to cases where assert \texttt{\color[HTML]{CB0000} failure} occurs for \texttt{no optimization} case}
		\label{}
		\begin{tabular}{ c | c | c | c | c } 
			\toprule
			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
			\hline\hline
			49999 & 50000 & 1.0000000000 & 0 & 0.0000000000 \\ \hline 
			12798121 & 50000 & 0.0039072461 & 121 & 254.9347362328 \\ \hline 
			2118330 & 50000 & 0.0234384766 & 3 & 41.6648888947 \\ \hline 
			3191133 & 50000 & 0.0156259844 & 27 & 62.9959681516 \\ \hline 
			1592312 & 50000 & 0.0312509687 & 85 & 30.9990080819 \\ \hline 
			802573 & 50000 & 0.0625009375 & 6 & 14.9997600036 \\ \hline  
			404577 & 50000 & 0.1250008750 & 3 & 6.9999440004 \\ \hline 
			199379 & 50000 & 0.2500007500 & 2 & 2.9999880000 \\ \hline 
			133424 & 50000 & 0.3750006250 & 1 & 1.6666622222 \\ \hline 
			99661 & 50000 & 0.5000005000 & 0 & 0.9999980000 \\ \hline 
			\bottomrule
		\end{tabular}
	\end{table}
	\begin{table}
		\centering
		\caption{Comparing \texttt{prob(p)} value to cases where assert \texttt{\color[HTML]{036400} passed} without \texttt{optimization} step.}
		\label{}
		\begin{tabular}{ c | c | c | c | c } 
			\toprule
			\texttt{Flip Runs} & \texttt{Program Runs}& \texttt{prob(p)} & \texttt{z (Last)} & \texttt{(1-p)/p} \\ 
			\hline\hline
			2551264 & 50000 & 0.0195322305 & 60 & 50.1974298071 \\ \hline 
			6371788 & 50000 & 0.0078134922 & 169 & 126.9837458595 \\ \hline 
			4280156 & 50000 & 0.0117197383 & 303 & 84.3261373592 \\ \hline 
			1592312 & 50000 & 0.0312509687 & 85 & 30.9990080819 \\ \hline
			266112 & 50000 & 0.1875008125 & 7 & 4.3333102223 \\ \hline 
			\bottomrule
		\end{tabular}
	\end{table}
\end{document}

>>>>

\begin{document}
	\begin{figure}
		\begin{minted}{python}
	def ex7(inpt):
		x = 0
		n = 10  # N This is a forall.
		y = 10  # N This is a forall.
		prob = inpt[0] # This is a forall. 
		while(n > 0):
			d = bernoulli.rvs(size=1, p=prob)[0]
			if(d): 
				x = x + y # x is probabilistic here
			n = n-1
		return x

	# Expected Value of "x"
	# E[x] = prob * n * y
	assert((P(x - (prob * n * y)) <= 0) <= 0.6)
		\end{minted}
		\caption{Program listing for finding probabilistic \texttt{assert} violation.}
	\end{figure}
	\begin{figure}
	\begin{minted}{python}
		(0.0000001 < prob_sym),
		(1 <= y_sym),
		(prob_sym <= 1),
		(10 <= n_sym)
	\end{minted}
	\caption{Constraints on \texttt{Path-1} where control flow is in the \texttt{while} loop.}
	\end{figure}
	\begin{figure}
		\begin{minted}{python}
		(0.0000001 < prob_sym),
		(1 <= y_sym),
		(prob_sym <= 1),
		n_sym == 0 # Exit from Loop
		\end{minted}
		\caption{Constraints on \texttt{Path-2} where control flow exits the \texttt{while} loop.}
	\end{figure}
\begin{figure}
	\begin{minted}{c}
	double prob;
	int x, n, y;

	// forall variables
	klee_make_symbolic(&y, sizeof(y), "y_sym");
	klee_make_symbolic(&n, sizeof(n), "n_sym");
	make_pse_symbolic(&prob, sizeof(prob), "prob_sym", 0, 1);

	// Some restrictions on the values.
	klee_assume(y >= 0);
	klee_assume(10 <= n);

	// Work around for silent concretization of prob.
	prob = 0.5;

	// Prob Sym Variables.
	make_pse_symbolic(&x, sizeof(x), "x_pse_sym", 0, 2147483647);

	std::default_random_engine generator;
	std::bernoulli_distribution bernoulli_rvs(prob);

	// This is the "inner" loop which affects the final value of "x".
	while (n > 0)
	{
		int d = bernoulli_rvs(generator);
		if (d)
			x = x + y;
		n = n - 1;
	}

	return 0;
	\end{minted}
	\caption{\texttt{KLEE Transformation} of the program for testing the \texttt{assert}. }
\end{figure}

	\begin{figure}
		\begin{minted}{c}
	long double prob;
	int x, n, y, n_start, y_start;
	long long unsigned int win = 0, loop_run = 0, prob_runs = 0;

	scanf("%d", &n);
	scanf("%d", &y);
	scanf("%Lf", &prob);

	n_start = n;
	y_start = y;

	while (termCount--)
	{
		x = 0;
		int n_loop = n; // maintain "n" for re-runs of loop.

		// program execution
		std::default_random_engine generator;
		std::bernoulli_distribution bernoulli_rvs(prob);

		// "n" gets changed, we need to maintain the loop. 
		while (n_loop > 0)
		{
			int d = bernoulli_rvs(generator);
			if (d)
			{
				// This doesn't favours the "win" condition.
				x = x + y;
			}
			n_loop -= 1;

			// Iterations of the inner loop.
			// How many times the probabilistic loop gets executed?
			prob_runs++;
		}

		// Sample for probability. This is the assert condition.
		if ((double)x - (prob * n * y) <= 0)
			win++;

		// No. of times the program gets executed.
		loop_run++;
	}
		\end{minted}
		\caption{Testing \texttt{Translate()} of the program for testing the \texttt{assert}. }
	\end{figure}
	\begin{table}
		\centering
		\caption{Comparing \texttt{prob(p)} value Vs \texttt{assert} status for low values of \texttt{prob(p)} shown for limited iterations.}
		\label{}
		\begin{tabular}{ c | c | c | c | c | c | c } 
			\toprule
			\texttt{prob-value} & \texttt{Program Runs}& \texttt{Loop Runs} & \texttt{Wins} & \texttt{P((x - (prob * n * y)) <= 0)}  & \texttt{n} & \texttt{y} \\ 
			\hline\hline
			0.0000001298 & 100000 & 5600000 & 100000 & 1.000000 & 56 & 21 \\ \hline
			0.0000001596 & 100000 & 4000000 & 100000 & 1.000000 & 40 & 17 \\ \hline
			0.0000003384 & 100000 & 3600000 & 100000 & 1.000000 & 36 & 28 \\ \hline
			0.0000039147 & 100000 & 2800000 & 100000 & 1.000000 & 28 & 18 \\ \hline
			0.0000077294 & 100000 & 2300000 & 100000 & 1.000000 & 23 & 24 \\ \hline
			0.0000153588 & 100000 & 2700000 & 100000 & 1.000000 & 27 & 16 \\ \hline
			0.0000306176 & 100000 & 2100000 & 100000 & 1.000000 & 21 & 15 \\ \hline
			0.0000611352 & 100000 & 2200000 & 100000 & 1.000000 & 22 & 14 \\ \hline
			0.0001221703 & 100000 & 2000000 & 100000 & 1.000000 & 20 & 11 \\ \hline
			0.0002442406 & 100000 & 2600000 & 100000 & 1.000000 & 26 & 10 \\ \hline
			0.0004883812 & 100000 & 1900000 & 100000 & 1.000000 & 19 & 13 \\ \hline
			0.0009766624 & 100000 & 1800000 & 100000 & 1.000000 & 18 & 9 \\ \hline
			0.0019532248 & 100000 & 2500000 & 100000 & 1.000000 & 25 & 12 \\ \hline
			0.0039063496 & 100000 & 2400000 & 100000 & 1.000000 & 24 & 8 \\ \hline
			{\textbf{ \color[HTML]{036400} 0.0078125992}} & {\textbf{\color[HTML]{036400} 100000}} & {\textbf{\color[HTML]{036400} 1700000}} & {\textbf{\color[HTML]{036400} 0}} & {\textbf{\color[HTML]{036400} 0.000000}} & {\textbf{\color[HTML]{036400} 17}} & {\textbf{\color[HTML]{036400} 7}} \\ \hline
			0.0156250984 & 100000 & 1600000 & 0 & 0.000000 & 16 & 5 \\ \hline
			0.0312500969 & 100000 & 1400000 & 0 & 0.000000 & 14 & 6 \\ \hline
			0.0625000937 & 100000 & 1300000 & 0 & 0.000000 & 13 & 4 \\ \hline
			0.2500000750 & 100000 & 1100000 & 0 & 0.000000 & 11 & 2 \\ \hline
			0.5000000500 & 100000 & 1000000 & 0 & 0.000000 & 10 & 1 \\ \hline
			\bottomrule
		\end{tabular}
	\end{table}
	\begin{figure}
\begin{minted}{python}
	(0.0075243180 < prob_sym),
	(1 <= y_sym),
	(prob_sym <= 0.0078125992),
	(10 <= n_sym)
	\end{minted}
	\caption{Narrowing constraints on \texttt{Path-1} where control flow is in the \texttt{while} loop.}
\end{figure}
\begin{table}
	\centering
	\caption{Comparing \texttt{prob(p)} value to cases Vs \texttt{assert} status for low values of \texttt{prob(p)} on narrowing}
	\label{}
	\begin{tabular}{ c | c | c | c | c | c | c } 
		\toprule
		\texttt{prob-value} & \texttt{Program Runs}& \texttt{Loop Runs} & \texttt{Wins} & \texttt{P((x - (prob * n * y)) <= 0)}  & \texttt{n} & \texttt{y} \\ 
		\hline\hline
		0.0068589250 & 100000 & 2500000 & 100000 & 1.000000 & 25 & 12 \\ \hline
		0.0068665544 & 100000 & 1600000 & 100000 & 1.000000 & 16 & 5 \\ \hline
		0.0068970719 & 100000 & 1400000 & 100000 & 1.000000 & 14 & 6 \\ \hline
		0.0069581071 & 100000 & 1300000 & 100000 & 1.000000 & 13 & 4 \\ \hline
		0.0070801774 & 100000 & 1200000 & 100000 & 1.000000 & 12 & 3 \\ \hline
		0.0073243180 & 100000 & 1100000 & 100000 & 1.000000 & 11 & 2 \\ \hline
		{\textbf{ \color[HTML]{036400} 0.0078125992}} & {\textbf{\color[HTML]{036400} 100000}} & {\textbf{\color[HTML]{036400} 1700000}} & {\textbf{\color[HTML]{036400} 0}} & {\textbf{\color[HTML]{036400} 0.000000}} & {\textbf{\color[HTML]{036400} 17}} & {\textbf{\color[HTML]{036400} 7}} \\ \hline
		0.0156250984 & 100000 & 1600000 & 0 & 0.000000 & 16 & 5 \\ \hline
		\bottomrule
	\end{tabular}
\end{table}
\begin{table}
	\centering
	\caption{Comparing \texttt{prob(p)} value to cases Vs \texttt{assert} status for low values of \texttt{prob(p)} on further narrowing}
	\label{}
	\begin{tabular}{ c | c | c | c | c | c | c } 
		\toprule
		\texttt{prob-value} & \texttt{Program Runs}& \texttt{Loop Runs} & \texttt{Wins} & \texttt{P((x - (prob * n * y)) <= 0)}  & \texttt{n} & \texttt{y} \\ 
		\hline\hline
		0.0075603531 & 100000 & 1300000 & 100000 & 1.000000 & 13 & 4 \\ \hline
		0.0075963883 & 100000 & 1200000 & 100000 & 1.000000 & 12 & 3 \\ \hline
		0.0076684586 & 100000 & 1100000 & 100000 & 1.000000 & 11 & 2 \\ \hline
		0.0077243207 & 100000 & 2100000 & 0 & 0.000000 & 21 & 24 \\ \hline
		0.0077243234 & 100000 & 2800000 & 0 & 0.000000 & 28 & 16 \\ \hline
	{\textbf{ \color[HTML]{036400} 0.0078125992}} & {\textbf{\color[HTML]{036400} 100000}} & {\textbf{\color[HTML]{036400} 1700000}} & {\textbf{\color[HTML]{036400} 0}} & {\textbf{\color[HTML]{036400} 0.000000}} & {\textbf{\color[HTML]{036400} 17}} & {\textbf{\color[HTML]{036400} 7}} \\ \hline
		\bottomrule
	\end{tabular}
\end{table}
\end{document}
